Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-10-04 supplement/06_bat_data.Rmd
select movements away from roost

# get hour of day to filter for nighttime
data_residence[, hour := data.table::hour(ts)]

>>>>

# get hour of day to filter for nighttime
data_residence[, hour := data.table::hour(ts)]
```

### Movements away from the roost

To focus on night-time bat foraging around fruit trees, we shall filter data _both_ on the timestamps, to select night-time positions, and on the locations, to select positions > 1 km away from the roost-cave at Har Gershom (see main text Fig. 8).

Combining these two filters allows us to exclude bat positions at the roost-cave that may be due to individual-differences in bats' departure or return times to and from their foraging areas.

```{r}
# read in roosts and select the Har Gershom roost
roosts = fread("data/Roosts.csv")
setnames(roosts, "Species", "roost_name")
roosts = roosts[roost_name == "Har Gershom"]

# define a simple distance function that is vectorised
get_distance_adhoc = function(x1, y1, x2, y2) {
  sqrt(((x2 - x1) ^2) + ((y2 - y1) ^2) )
}

# calculate distance to roost cave at Har Gershom
data_residence[, distance_roost := get_distance_adhoc(
  x1 = roosts$X, 
  x2 = data_residence$X, 
  y1 = roosts$Y, 
  y2 = data_residence$Y
)
]

# plot for sanity check --- this plot is not shown
fig_roost_exclude =
  ggplot(data_residence)+
  geom_point(
    aes(X, Y, col = distance_roost)
  )+
  geom_point(
    data = roosts,
    aes(X, Y),
    shape = 21, size = 4,
    fill = "blue",
    alpha = 0.5
  )+
  scale_colour_viridis_c(
    option = "B", direction = -1,
    trans = "log10",
    breaks = c(1000, 2500, 5000),
    labels = function(x) {
      scales::comma(
        x,
        scale = 0.001, suffix = "km"
      )
    },
    limits = c(1000, NA),
    na.value = "lightblue"
  )+
  ggspatial::annotation_scale(location = "br") +
  theme_test() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank(),
    legend.position = "top",
    legend.key.height = unit(2, "mm"),
    legend.title = element_text(vjust = 1)
  ) +
  coord_sf(
    crs = 2039
  )+
  labs(
    colour = "distance (km)"
  )
```
